---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# typogenerator: Several Mechanisms for Typo Generation

<!-- badges: start -->

 [![License](https://img.shields.io/badge/License-Apache%202.0-blue.svg)](https://choosealicense.com/licenses/apache-2.0/) ![CRAN status](https://www.r-pkg.org/badges/version/typogenerator) [![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![codecov](https://codecov.io/gh/mikemahoney218/typogenerator/branch/master/graph/badge.svg)](https://codecov.io/gh/mikemahoney218/typogenerator) [![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip) [![R build status](https://github.com/mikemahoney218/typogenerator/workflows/R-CMD-check/badge.svg)](https://github.com/mikemahoney218/typogenerator/actions) 

<!-- badges: end -->

## Overview

This package is an R implementation of the Golang
[Typogenerator](https://github.com/zntrio/typogenerator) library, incorporating
several methods for creating typos from a set of input strings.

All of these methods work on character vectors of any length and have a standard
interface via the `typo_*` functions:

```{r}
library(typogenerator)

typo_hyphenation("lip")

typo_transposition(c("cats", "dogs"))
```

In addition, generating typos via multiple methods can be done easily using the
`generate_typos` function:

```{r}
generate_typos("snow", c("typo_addition", "typo_prefix"))
```

By default, these functions will only use characters already inside of the word
or which are generally accepted as file names on English-based systems, but 
users can define their own character options by passing vectors to the `chars` 
arguments of each function.

Note that this package is in very early development and the user-facing API is 
liable to change.

## Installation

You can install the development version of terrainr from [GitHub](https://github.com/mikemahoney218/typogenerator) with:

``` r
# install.packages("devtools")
devtools::install_github("mikemahoney218/typogenerator")
```
